Title

### 2018-09-09 thesis/paper/paper.tex
Modified paper with rule part removal

\paragraph{Rules}
The \emph{value requires statement} constraint is syntactically very similar to the previous \emph{item requires statement} constraint. Instead of requiring a statement on the item of a constrained statement it requires it on the value. Inequality need to be computed between all properties and all values and the item statement order established. The conjunctions change in the first statement and are:
\begin{equation*}
\begin{split}
c_1 = &\text{statement\_EDB}(Q, R, \text{propertyConstant}, I) \wedge{} \\
&\text{statement\_EDB}(S, I, P, V) \wedge \text{unequal}(\text{requiredPropertyConstant}, P)
\end{split}
\end{equation*} \(\)
\begin{equation*}
\begin{split}
c_2 = &\text{statement\_EDB}(Q, R, \text{propertyConstant}, I) \wedge{} \\
&\text{statement\_EDB}(S, I, \text{requiredPropertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
The final violation rule would then be:
\begin{equation*}
\begin{split}
\text{violation\_statement}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statement\_EDB}(S, I, \text{propertyConstant}, V) \wedge{} \\
&\text{statement\_EDB}(O, V, P, X) \wedge \text{last}(O, V) \wedge{} \\
&\text{require}(O, \text{propertyConstant}, \text{requiredPropertyConstant})
\end{split}
\end{equation*}

>>>>

\paragraph{Rules}
The \emph{value requires statement} constraint is syntactically very similar to the previous \emph{item requires statement} constraint. Instead of requiring a statement on the item of a constrained statement it requires it on the value. Inequality need to be computed between all properties and all values and the item statement order established. The conjunctions change in the first statement and are:
\begin{equation*}
\begin{split}
c_1 = &\text{statement\_EDB}(Q, R, \text{propertyConstant}, I) \wedge{} \\
&\text{statement\_EDB}(S, I, P, V) \wedge \text{unequal}(\text{requiredPropertyConstant}, P)
\end{split}
\end{equation*} \(\)
\begin{equation*}
\begin{split}
c_2 = &\text{statement\_EDB}(Q, R, \text{propertyConstant}, I) \wedge{} \\
&\text{statement\_EDB}(S, I, \text{requiredPropertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
The final violation rule would then be:
\begin{equation*}
\begin{split}
\text{violation\_statement}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statement\_EDB}(S, I, \text{propertyConstant}, V) \wedge{} \text{last}(O, V) \wedge{} \\
&\text{require}(O, \text{propertyConstant}, \text{requiredPropertyConstant})
\end{split}
\end{equation*}
